Academic Advancement Advice: Author Articles as A.~A.

### 2018-04-01 trunk/citations/paper.tex
Submitted version

@@

\begin{tabular}{l|l|l|l}
{\bf word} & {\bf articles} & {\bf citations} & {\bf E = c/a} \\
  \hline
folin & 172 & 209,642 & 1,211.8 \\
power/knowledge & 111 & 55,992 & 499.9 \\
\{s\} & 101 & 38,241 & 374.9 \\
1972-1977 & 171 & 54,917 & 319.2 \\
\textbackslash sqrt\{s\} & 126 & 33,253 & 261.8 \\
eigenfaces & 176 & 45,284 & 255.8 \\
america''s & 119 & 30,478 & 253.9 \\
gromacs & 125 & 30,865 & 244.9 \\
neo-ffi & 102 & 21,992 & 213.5 \\
esh & 156 & 33,142 & 211.1 \\
\end{tabular}

These are mostly explained by being relatively rare words that appear
in extremely popular papers. For example, {\em folin} comes from a
1951 paper\cite{lowry1951protein} describing a procedure for using
this reagent, which I guess everyone who uses this technique cites
(Google scholar has this paper at 215,329 citations). {\em
  Power/knowledge} and {\em 1972-1977} both come from the title of a
Foucault book\cite{foucault1980power} with 31,590 citations.

@@

\begin{tabular}{l|l|l|l}
\,  & artices & citations & multiplier \\
  \hline
of & 64322278 & 366756237 & 1.207822 \\
and & 42576889 & 276526184 & 1.375780 \\
in & 39685539 & 230534759 & 1.230526 \\
the & 38873614 & 216491707 & 1.179704 \\
a   & 22666824 & 139244700 & 1.301292 \\
for & 19048050 & 114197875 & 1.269972 \\
on & 15194275 & 68904896 & 0.960631 \\
with & 10825547 & 60752792 & 1.188784 \\
to & 10202749 & 58590695 & 1.216461 \\
de & 7753205 & 3283786 & 0.089718 \\
by & 7259598 & 42234470 & 1.232370 \\
from & 5389957 & 35999433 & 1.414806 \\
an & 5368923 & 33088995 & 1.305519 \\
la & 4417389 & 1471023 & 0.070541 \\
study & 4370395 & 22022172 & 1.067397 \\
\end{tabular}

Several of these words are visible in Figure~\ref{fig:wordcdf}, in
fact; they are so common that they cause large jumps in both article
and citation count. Curiously, most of the common words have a
multiplier greater than 1; they {\em increase} the expected number of
citations. {\em of} sounds smart (e.g. {\em Of Mice And Men}), {\em
  and} makes sense (paper contains at least two results). On the other
hand, {\em on} actually reduces the citation count, probably because
it implies equivocation (e.g. {\em On the other hand}). Dramatically,
common non-English words have very low multipliers; Spanish words {\em
  de} and {\em la} reduce citations by a factor of more than ten. This
may be due to problems in the data set, but it is certainly easy to
imagine real cultural bias!

Finally, here are the words with the worst multipliers:
\begin{tabular}{l|l|l|l}
313779.  \includegraphics[width=2em]{bookreview} & 29582 & 1 & 0.000068 \\
313778.  \includegraphics[width=5em]{interview} & 20547 & 1 & 0.000097 \\
313777.  facharzt & 85315 & 9 & 0.000117 \\
313776.  f3d & 125257 & 15 & 0.000128 \\
313775.  recenzja & 63568 & 8 & 0.000142 \\
313774.  newhaven & 13296 & 1 & 0.000150 \\
313773.  secr\'etaire & 12267 & 1 & 0.000163 \\
313772.  zahnarzt & 17958 & 2 & 0.000167 \\
313771.  libguides & 389727 & 72 & 0.000187 \\
313770.  \includegraphics[width=2em]{research} & 12961 & 2 & 0.000231 \\
313769.  \includegraphics[width=1em]{that} & 15984 & 3 & 0.000250 \\
313768.  kitas & 7713 & 1 & 0.000259 \\
% 313767.  シンポジウム & 18539 & 4 & 0.000270 \\
% 313766.  特集 & 878011 & 240 & 0.000274 \\
\end{tabular}

@@

(Of course I am just poking fun, not seriously declaring these
articles somehow ``worst.'' Many good articles are never cited. For
example, as far as I know, the paper you are reading right now has no
citations.)

One way to do this is to try to estimate the number of citations that
a paper will get based on the words in its title. Since we already
collected the words that are most citable, this is an apparently
simple affair. We can estimate the citation rate by just taking the
product of the multipliers for the words. We treat words for which
we don't have data (because they didn't meet thresholds) as having
multiplier 1.

This first cut has some problems. As an illustration, the article
with the highest estimated citation rate (among those with zero actual
citations) is a paper\cite{leigland2009grid} called
\begin{quote}
Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid
\end{quote}
which is expected to have 5,262,751,498,750,000,000,000,000 citations.
This is because the word {\em grid} has a favorable multiplier and is
repeated 121 times.

@@

The first is probably not the title of an article\cite{officehours},
although we can agree that it is unlikely to be cited. The second is
probably a bad entry, with the entire citation packed into the title
field. This book~\cite{o1997thomas} actually does have 94 citations
(or DOES IT?) on Google Scholar and an Amazon Sales Rank of \#10,837
in {\em Christian Denominations \& Sects}.\footnote{ On the other
  hand, the entry does have a different
  author\cite{stevenson2000thomas}, so it could possibly be a review
  of this book whose title is literally the string above, including
  the price?} In order to prevent such data problems from affecting
our results, I then added a requirement that the article have basic
metadata (either a Digital DOI Identifier field or {\tt venue}) for it
to be considered. There vast majority still appear to be broken
entries, but picking through the results I'm finally able to find what
appear to be actual articles:

@@

The first is definitely a real article~\cite{bedient1974eight}---which
apparently has 95 citations on Google Scholar---so the estimate failed
us here. It's easy to see why it has such a bad score, though; it's
packed with people's names and initials, just like the scores of
uncited book reviews and other broken citations. The second is also a
real tribute to this Nobel prize winner~\cite{loewi195580th} with 5
citations that Google knows of. Again it contains names and
appelations that look like initials.

>>>>

\usepackage{nopageno}

@@

\begin{tabular}{l|l|l|l}
{\bf word} & {\bf articles} & {\bf citations} & {\bf E = c/a} \\
  \hline
folin & 172 & 209,642 & 1,211.8 \\
power/knowledge & 111 & 55,992 & 499.9 \\
\{s\} & 101 & 38,241 & 374.9 \\
1972-1977 & 171 & 54,917 & 319.2 \\
\textbackslash sqrt\{s\} & 126 & 33,253 & 261.8 \\
eigenfaces & 176 & 45,284 & 255.8 \\
america''s & 119 & 30,478 & 253.9 \\
gromacs & 125 & 30,865 & 244.9 \\
neo-ffi & 102 & 21,992 & 213.5 \\
esh & 156 & 33,142 & 211.1 \\
eqs & 128 & 25,504 & 197.7 \\
charmm & 175 & 31,579 & 179.4 \\
position-specific & 378 & 67,250 & 177.4 \\
kegg & 201 & 32,989 & 163.3 \\
arlequin & 161 & 26,318 & 162.4 \\
praat & 158 & 25,217 & 158.6 \\
\end{tabular}

These are mostly explained by being relatively rare words that appear
in extremely popular papers. For example, {\em folin} comes from a
1951 paper\cite{lowry1951protein} describing a procedure for using
this reagent, which I guess everyone who uses this technique cites
(Google scholar has this paper at 215,329 citations). {\em
  Power/knowledge} and {\em 1972-1977} both come from the title of a
Foucault book\cite{foucault1980power} with 31,590 citations. {\tt
  america''s} is not a LaTeX disaster; it really has two apostrophes
in it, and it is weird that this typo appears in 119 articles.

@@

\begin{tabular}{l|l|l|l}
\,  & artices & citations & multiplier \\
  \hline
1. of & 64,322,278 & 366,756,237 & 1.207822 \\
2. and & 42,576,889 & 276,526,184 & 1.375780 \\
3. in & 39,685,539 & 230,534,759 & 1.230526 \\
4. the & 38,873,614 & 216,491,707 & 1.179704 \\
5. a   & 22,666,824 & 139,244,700 & 1.301292 \\
6. for & 19,048,050 & 114,197,875 & 1.269972 \\
7. on & 15,194,275 & 68,904,896 & 0.960631 \\
8. with & 10,825,547 & 60,752,792 & 1.188784 \\
9. to & 10,202,749 & 58,590,695 & 1.216461 \\
10. de & 7,753,205 & 3,283,786 & 0.089718 \\
11. by & 7,259,598 & 42,234,470 & 1.232370 \\
12. from & 5,389,957 & 35,999,433 & 1.414806 \\
13. an & 5,368,923 & 33,088,995 & 1.305519 \\
14. la & 4,417,389 & 1,471,023 & 0.070541 \\
15. study & 4,370,395 & 22,022,172 & 1.067397 \\
\end{tabular}

Several of these words are visible in Figure~\ref{fig:wordcdf}, in
fact; they are so common that they cause large jumps in both article
and citation count. Curiously, most of the common words have a
multiplier greater than 1; they {\em increase} the expected number of
citations. {\em Of} sounds smart (e.g. {\em Of Mice And Men}), {\em
  and} makes sense (paper contains at least two results). On the other
hand, {\em on} actually reduces the citation count, probably because
it implies equivocation (e.g. {\em On the other hand}). Dramatically,
common non-English words have very low multipliers; Spanish words {\em
  de} and {\em la} reduce citations by a factor of more than ten. This
may be due to problems in the data set, but it is certainly easy to
imagine real cultural bias!

Finally, here are the words with the worst multipliers:
\begin{tabular}{l|l|l|l}
313779.  \includegraphics[width=2em]{bookreview} & 29,582 & 1 & 0.000068 \\
313778.  \includegraphics[width=5em]{interview} & 20,547 & 1 & 0.000097 \\
313777.  facharzt & 85,315 & 9 & 0.000117 \\
313776.  f3d & 125,257 & 15 & 0.000128 \\
313775.  recenzja & 63,568 & 8 & 0.000142 \\
313774.  newhaven & 13,296 & 1 & 0.000150 \\
313773.  secr\'etaire & 12,267 & 1 & 0.000163 \\
313772.  zahnarzt & 17,958 & 2 & 0.000167 \\
313771.  libguides & 389,727 & 72 & 0.000187 \\
313770.  \includegraphics[width=2em]{research} & 12,961 & 2 & 0.000231 \\
313769.  \includegraphics[width=1em]{that} & 15,984 & 3 & 0.000250 \\
313768.  kitas & 7,713 & 1 & 0.000259 \\
% 313767.  シンポジウム & 18539 & 4 & 0.000270 \\
% 313766.  特集 & 878011 & 240 & 0.000274 \\
\end{tabular}

@@

(Of course: In case someone who wrote one of these papers finds
themselves here, please note that I am just poking fun, not seriously
declaring these articles somehow ``worst.'' Many good articles are
never cited. For example, as far as I know, the paper you are reading
right now has no citations.)

One way to do this is to try to estimate the number of citations that
a paper will get based on the words in its title. Since we already
collected citation multipliers for all words, this is an apparently
simple affair. We can estimate the citation rate by just taking the
product of the multipliers for the words. We treat words for which we
don't have data (because they didn't meet thresholds) as having
multiplier 1.

This first cut has some problems. As an illustration, the article
with the highest estimated citation rate (among those with zero actual
citations) is a paper\cite{leigland2009grid} called
\begin{quote}
Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid Grid
\end{quote}
which according to the analysis is expected to have 5,262,751,498,750,000,000,000,000 citations.
This is because the word {\em grid} has a favorable multiplier and is
repeated 121 times.

@@

The first is probably not the title of an article\cite{officehours},
although we can agree that it is unlikely to be cited. The second is
probably a bad entry, with the entire citation packed into the title
field. This book actually does have 94 citations
(or DOES IT?~\cite{o1997thomas}) on Google Scholar and an Amazon Sales Rank of \#10,837
in {\em Christian Denominations \& Sects}.\footnote{ On the other
  hand, the entry does have a different
  author\cite{stevenson2000thomas}, so it could possibly be a review
  of this book whose title is literally the string above, including
  the price?} In order to prevent such data problems from affecting
our results, I then added a requirement that the article have basic
metadata (either a Digital DOI Identifier field or {\tt venue}) for it
to be considered. There vast majority still appear to be broken
entries, but picking through the results I'm finally able to find what
appear to be actual articles:

@@

I don't know about you but I fell asleep just reading the titles. The
first is definitely a real article~\cite{bedient1974eight}---which
apparently has 95 citations on Google Scholar---so the estimate failed
us here. It's easy to see why it has such a bad score, though; it's
packed with people's names and initials, just like the scores of
uncited book reviews and other broken citations. The second is also a
real tribute to this Nobel prize winner~\cite{loewi195580th} with 5
citations that Google knows of. Again it contains names and
appelations that look like initials.
